Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-03 documentation/paper.tex
Mentioned performance with position corrections; fixed some statistics

Once the audio was cropped properly, $DeepConv(\omega)$ achieved a maximum of 77\% accuracy on validation data. Using the same network architecture (except for the input layer), $DeepConvWithPos(\omega, \chi)$ managed 85\%. The maximum obtained on a grid search with position correction was 90\%. While this is not a drastic improvement, it is a fairly strong indication that the network is able to extract meaningful information from the position, which may be used in an internal position correction of the volume. That said, neither of these accuracy statistics are particularly good, which does not bode well for this input format as a whole.

@@

It became evident very quickly that a high resolution was not required to get a high accuracy relative to the ground truth data. A perceptron trained on $\beta_{8}$ managed an excellent 97\% validation accuracy by this metric. Increasing the number of bands seemed initially not to provide any improvement; the best accuracy reached with $\beta_{20}$ was 93\%, and with $\beta_{40}$ it was 94\%.

>>>>

Once the audio was cropped properly, $DeepConv(\omega)$ achieved a maximum of 77\% accuracy on validation data. Using the same network architecture (except for the input layer), $DeepConvWithPos(\omega, \chi)$ managed 85\%. The maximum obtained on a grid search with position correction was 91\%. While this is not a drastic improvement, it is a fairly strong indication that the network is able to extract meaningful information from the position, which may be used in an internal position correction of the volume. That said, neither of these accuracy statistics are particularly good, which does not bode well for this input format as a whole.

@@

It became evident very quickly that a high resolution was not required to get a high accuracy relative to the ground truth data. A perceptron trained on $\beta_{8}$ managed an excellent 98\% validation accuracy by this metric. Increasing the number of bands seemed initially not to provide any improvement; the best accuracy reached with $\beta_{20}$ was 93\%, and with $\beta_{40}$ it was 94\%.

Unlike for the convolutional neural network trained on $\omega$, wall cuts did not improve performance at all. While $FourierMLP(\beta_{N})$ peaked at 98\% validation accuracy, $FourierMLPWithPos(\beta_{N})$ reached only 95\%. Nevertheless, they both performed better than any of the network architectures trained on $\omega$.
